CODE CHECK

### 2020-05-11 codecheck-paper.Rmd
Update codecheck-paper.Rmd

- role of data and code, data science
- reproducible resarch
- data enclaves
- CASCAID
- ROpenSci/PyOpenSci
- time capsules > https://twitter.com/DougBlank/status/1135904909663068165?s=09

>>>>

- role of data and code, data science
- reproducible resarch
- data enclaves
- CASCAID
- ROpenSci/PyOpenSci
- time capsules > https://twitter.com/DougBlank/status/1135904909663068165?s=09
- science is changing: https://theconversation.com/what-you-need-to-know-about-how-coronavirus-is-changing-science-137641
